---
title: "Data Preparation"
author: "Dana Swarbrick"
date: "10/11/2021"
output: html_document
---

Note: originally this document was named "Virtual_Participants.Rmd" but it became the entire data preparation script.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import libraries

```{r libraries}
packages = c("readxl", "magrittr", "reshape2","ggpubr", "ltm","janitor", "PerformanceAnalytics","lme4", "openxlsx","psych", "tidyverse")

## Now load or install&load all
package.check <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  }
)

source("useful_functions.R")
```

# Virtual Participants
## Import data

```{r dansk-files}
setwd('../experimental-data/surveys/')
filenames <- list.files(pattern="*Dansk.xlsx", full.names=TRUE)
ldf<-lapply(filenames, read_xlsx)
for (i in 1:length(ldf))
  assign(paste("dansk.df", i, sep=""), ldf[[i]])
```
```{r english-files}
setwd('../experimental-data/surveys/')
filenames <- list.files(pattern="*English.xlsx", full.names=TRUE)
ldf<-lapply(filenames, read_xlsx)
for (i in 1:length(ldf))
  assign(paste(paste("english.df", i, sep="")), ldf[[i]])
```

## Tidy & Rename
To avoid repeating everything 2x, will just combine english and danish surveys here. 

### Rename cols

#### Q1: Pre-concert Survey
```{r}
q1<-names(english.df1)
q1.dansk<-names(dansk.df1)
q1id<-c("NR", "userID", "city", "viewing_with_others", "age", "gender", "musician_status", "personal_relation", "fan", "EC_1", "EC_2", "EC_3", "EC_4", "EC_5", "EC_6", "EC_7","Elapsed_time")
codebook1<-data.frame(cbind(q1id,q1, q1.dansk))

# Rename cols based on codes
names(english.df1)<-q1id
names(dansk.df1)<-q1id
```

#### Q2, Q3, Q5: After Beethoven, Schnittke, Folk
```{r}
q2<-names(english.df2)
q3<-names(english.df3)
q5<-names(english.df5)

q2.dansk<-names(dansk.df2)
q3.dansk<-names(dansk.df3)
q5.dansk<-names(dansk.df5)
```

##### Check to make sure that the questions actually are all the same and in the same order
```{r}
q2==q3
q2[q2!=q3]
q3[q2!=q3]
q3==q5
q3[q5!=q3]
q5[q5!=q3]

qtest<-data.frame(cbind(q2,q3,q5))
#Looks good - just one inconsistency in wording.
```
##### And in danish
```{r}
q2.dansk==q3.dansk
q2.dansk[q2.dansk!=q3.dansk]
q3.dansk[q2.dansk!=q3.dansk]
q3.dansk==q5.dansk
q3.dansk[q5.dansk!=q3.dansk]
q5.dansk[q5.dansk!=q3.dansk]
```
This shows that there are no discrepancies between the wording of the questions across the surveys.

##### List of question IDs
Rename questions to question IDs.
```{r}
q2id<-c("NR", 
        "userID",
        "tears",
        "chills",
        "warm_feeling",
        "choked_up",
        "refreshed",
        "welcoming",
        "closeness",
        "positive",
        "negative", 
        "tense",
        "relaxed",
        "alone",
        "untouched",
        "moved",
        "touched",
        "admiration",
        "presence_grand",
        "greater_than_myself",
        "jaw_drop",
        "gasped",
        "challenge_process",
        "hard_comprehend",
        "others_moved",
        "connected_musicians",
        "connected_audience_streaming",
        "connected_audience_attending",
        "enjoy",
        "familiar",
        "own_world",
        "absorbed_music",
        "daydream",
        "sense_time",
        "distracted",
        "attentive",
        "attention_others",
        "attention_sensations",
        "positively_transformed",
        "negatively_transformed",
        "aware_body",
        "aware_movement",
        "aware_others_moving",
        "Elapsed_time")
```

```{r}
codebook2<-data.frame(cbind(q2id, q2, q2.dansk)) #don't need to repeat for 3 or 5
```

##### Rename cols in surveys
Since you checked, you can rename surveys q3 and q5 in the same way as well
```{r}
names(english.df2)<-q2id
names(english.df3)<-q2id
names(english.df5)<-q2id

#and danish
names(dansk.df2)<-q2id
names(dansk.df3)<-q2id
names(dansk.df5)<-q2id
```

#### Q4: Bach
```{r}
q4<-names(english.df4)
q4.dansk<-names(dansk.df4)
```

```{r}
q4id<-c("NR",
       "userID",
       "perceive",
       "instruments",
       "understanding",
       "augment",
       "disturb",
       "enhance", 
       "emotionally_moved",
       "familiar",
       "style", 
       "aware_body",
       "aware_movement",
       "aware_others_moving",
       "Elapsed_time")

codebook3<-data.frame(cbind(q4id, q4, q4.dansk))

names(english.df4)<-q4id
names(dansk.df4)<-q4id
```

#### Q6: After Concert Survey
```{r}
q6<-names(english.df6)
q6.dansk<-names(dansk.df6)
```

```{r}
q6id<-c("NR",
       "userID",
       "phone_loc",
       "aware_recording",
       "changed_behaviour",
       "Engage_1",
      "Engage_2",
      "Engage_3",
      "Engage_4",
      "Vis_Stim_1",
      "Vis_Stim_2",
      "Vis_Stim_3",
      "Vis_Stim_4",
      "Absorb_1",
      "Absorb_2",
      "Absorb_3",
      "Absorb_4",
      "Touch_1",
      "Touch_2",
      "Touch_3",
      "Touch_4",
      "AIMS_1",
      "AIMS_2",
      "AIMS_3",
      "AIMS_4",
      "AIMS_5",
      "AIMS_6",
      "AIMS_7",
      "AIMS_8",
      "AIMS_9",
      "AIMS_10",
      "AIMS_11",
      "AIMS_12",
      "AIMS_13",
      "AIMS_14",
      "AIMS_15",
      "AIMS_16",
      "AIMS_17",
      "AIMS_18",
      "AIMS_19",
      "AIMS_20",
      "AIMS_21",
      "AIMS_22",
      "AIMS_23",
      "AIMS_24",
      "AIMS_25",
      "AIMS_26",
      "AIMS_27",
      "AIMS_28",
      "AIMS_29",
      "AIMS_30",
      "AIMS_31",
      "AIMS_32",
      "AIMS_33",
      "AIMS_34",
      "Comments",
      "Elapsed_time")

codebook4<-data.frame(cbind(q6id, q6, q6.dansk))

names(english.df6)<-q6id
names(dansk.df6)<-q6id
```

### Label and combine English and Danish
```{r}
df.list = mget(paste0("english.df",1:6))
dfs.english = lapply(df.list, function(df) select(df,c(-"NR", -"Elapsed_time")))
df.list = mget(paste0("dansk.df",1:6))
dfs.dansk = lapply(df.list, function(df) select(df,c(-"NR", -"Elapsed_time")))

#explode list of dataframes to global vars
list2env(dfs.english,globalenv())
list2env(dfs.dansk,globalenv())

# add language to df1 (demographic info)
english.df1$language<-"English"
dansk.df1$language<-"Danish"

#### Label language in the other dfs
# initially we had a few pts who were getting NAs in the language column because some people hadn't filled df1
english.df2$language<-"English"
dansk.df2$language<-"Danish"
english.df3$language<-"English"
dansk.df3$language<-"Danish"
english.df4$language<-"English"
dansk.df4$language<-"Danish"
english.df5$language<-"English"
dansk.df5$language<-"Danish"
english.df6$language<-"English"
dansk.df6$language<-"Danish"

# Combine to larger dataframes
df1<-bind_rows(english.df1, dansk.df1)
df2<-bind_rows(english.df2, dansk.df2)
df3<-bind_rows(english.df3, dansk.df3)
df4<-bind_rows(english.df4, dansk.df4)
df5<-bind_rows(english.df5, dansk.df5)
df6<-bind_rows(english.df6, dansk.df6)
```
## Create a wide spreadsheet
### Label the repeated measures labels
```{r}
colnames(df2)[2:(ncol(df5)-1)]<-paste0(colnames(df2)[2:(ncol(df2)-1)], '_Beethoven')
colnames(df3)[2:(ncol(df5)-1)]<-paste0(colnames(df3)[2:(ncol(df3)-1)], '_Schnittke')
colnames(df5)[2:(ncol(df5)-1)]<-paste0(colnames(df5)[2:(ncol(df5)-1)], '_Folk')
```

### Combine into a wide spreadsheet
```{r}
df<-full_join(df1, df2, by =c("userID", "language"))
df<-full_join(df, df3, by =c("userID", "language"))
df<-full_join(df, df4, by =c("userID", "language"))
df<-full_join(df, df5, by =c("userID", "language"))
df<-full_join(df, df6, by =c("userID", "language"))
```

### check languages
```{r}
language_df<-df%>%select(userID, language)
```

## Data Cleaning
### Remove testing 
The first 5 rows are just garbage/testing from before the concert.
```{r}
df<-df%>%slice(6:nrow(df))

## Remove duplicate rows
df<-df%>% distinct()

### Continue to find and remove duplicates
# 1) Find rows that have the same userID as another row
duplicates<-df%>%
  group_by(userID)%>%
  filter(n() > 1)
#2) Check how many NAs are in each duplicate row
duplicates$nacount<- rowSums( !is.na(duplicates))

#3) Choose the rows with the highest number of non-NAs
dedup<-duplicates%>%group_by(userID)%>%
  slice(which.max(nacount))

#4) Replace these rows in the original dataframe
df<-df%>%filter(!userID %in% duplicates$userID)
dedup<-dedup%>%select(-nacount) # remove the nacount col
df<-df%>%bind_rows(dedup)

# There are two codes from the virtual participants who are not in the ParticipantCode spreadsheet:
## 1)  4e74e5b7-aa5b-3fba-2284-89bd559d8b02
## 2)  7e7716d5-77ef-a28a-c678-3223b5a6b62d

## This ID is a test: '7e7716d5-77ef-a28a-c678-3223b5a6b62d'
df<-df%>%filter(! userID == '7e7716d5-77ef-a28a-c678-3223b5a6b62d')

## And this ID is empty: '4e74e5b7-aa5b-3fba-2284-89bd559d8b02' 
df<-df%>%filter(! userID == '4e74e5b7-aa5b-3fba-2284-89bd559d8b02')
```

## Exclusion
We will exclude questionnaire data of participants who only filled survey 1 (and no other surveys) and who don't have sufficient motion data.
### 1) select participants who filled only survey 1
22 participants only filled survey 1.
```{r}
userID_list<-bind_rows(df2, df3, df4, df5, df6)%>%
  select(userID)

userID_list_df1<-df1%>%select(userID)

only_in_df1<-anti_join(userID_list_df1, userID_list)

only_in_df1_unique<-unique(only_in_df1)
# 22 participants only filled survey 1 and no other surveys.
```
### 2) Check if they have usable motion
16 participants only filled survey 1 and do not have usable motion. These 16 should be excluded from the data.
```{r}
# 2.1) Open spreadsheet from Finn
pt_codes<-read_xlsx("../experimental-data/DSQ_Audience_Map_newCodes.xlsx")
pt_codes<-pt_codes%>%rename(userID = "All DevID") 

# 2.2) retrieve the IDs for only people who should NOT be excluded.
usable_motion_df<-pt_codes%>%filter(Exclusion=="No") 

# list of those you need to exclude. 
exclude<-only_in_df1_unique%>%filter(! userID %in% usable_motion_df$userID)

# There are 16 participants who only filled survey 1 and who do not have usable motion.

# This also means that there are 6 participants who only filled survey 1 but who do have usable motion data. 

# See the section on "Remove Withdrawals" below where they are excluded. 
```

# Live Participants

## Format table
What format do these need to be in to allow cbind with the virtual surveys?
```{r paper-surveys}
setwd('../experimental-data/')
paper<-read_xlsx("Data_Paper_Surveys.xlsx")
```

```{r}
headers<-paper[1,]
headers[1,15:54]<-lapply(headers[1,15:54], function(x) paste0(x,"_Beethoven"))
headers[1,55:94]<-lapply(headers[1,55:94], function(x) paste0(x,"_Schnittke"))
headers[1,107:146]<-lapply(headers[1,107:146], function(x) paste0(x,"_Folk"))

headers<-unlist(headers)

# keep organizing the new dataframe and then  a full join or inner join should work to reveal what is missing
setwd('../experimental-data/')
live.df<-read_xlsx("Data_Paper_Surveys.xlsx", sheet = 1, skip = 2, col_names = headers, col_types="text")

# convert "NA" to real NA
live.df[live.df=="NA"]=NA

# add language column
live.df<-live.df%>%
  mutate(language = ifelse(startsWith(ID, "DSQd"), "Danish", "English")) # check<-live.df%>%select(ID,language) # double checked and it works 

# prepare for factoring musician status --> when pts checked off multipleboxes, this was averaged but for categorizing them we need to put them into a single categoruy so we could simply round I guess...
live.df$musician_status<-as.character(round(as.numeric(live.df$musician_status), digits = 0)) # rounded the number to nearest whole number

```
## Add the userID (device) col to the live participants spreadsheet
```{r}
id_codes<-pt_codes%>%select(userID, ParticipantCode, `Paper Q Codes`)
live.df<-left_join(live.df,id_codes, by = c("ID" = "Paper Q Codes"))
```

## Add ParticipantCode to the virtual participants spreadsheet
```{r}
df<-left_join(df,id_codes, by = "userID")
df<-df%>%filter(is.na(`Paper Q Codes`)) #this helped me discover there were 5 live participants that were labelled virtual because they must have filled one of the surveys on their phone. Removed them.
```

## Conduct a join to see which col names need to be changed
Also import all cols as char to enable the join with the df.
```{r}
live.df$group<-"Live"
df$group<-"Virtual"

# Check for differences before joining
test.df<-compare_df_cols(live.df, df) # looks great! (this helped me catch the language col issue and some other things)
```

```{r}
df.full.2<-full_join(live.df, df)
```

### Remove Withdrawals and Exclusions
Some participants requested withdrawal after the concert. 7 IDs with questionnaire results requested removal (their last request was for removal.) One is from before the copenhagen concert recording interval.
```{r}
withdraw<-c('22542356-471a-633f-c801-45a76f0b11cb','00afa8df-4bef-a5ae-55b2-44933117603a','dc381f4b-6a69-5a70-39f6-129568eaa6bc','83530137-77f7-afa8-b403-eee29ba8198f','6a917350-972c-f470-86e4-f4d548a6eddb','963dd442-f65f-d865-c73c-d461074631db','457b17cc-3b7d-ed41-5081-5969112cea4c')

#rmwd remove withdrawals
df.full.rmwd<-df.full.2%>%filter(! userID %in% withdraw) # this removed 5 pts, 4 of which had incomplete datasets, one had a full dataset.

#rmex: remove excluded participants (those who only filled survey 1 and did not have usable motion data).
df.full.rmex<-df.full.rmwd%>%filter(! userID %in% exclude$userID) 

df.full<-df.full.rmex
```

## Translations and factor
Factor these vars so that it will convert the norsk to the english
```{r}
df.full$gender<-fct_collapse(df.full$gender, Man = c("Man", "Mand", "1"), Woman = c("Woman", "Kvinde", "2"), "Choose Not to Identify" = c("Choose not to Identify", "3"), Other = c("Other", "4"))

df.full$musician_status<-fct_collapse(df.full$musician_status,"Tone-deaf" = c("1", "Tone-deaf", "Tonedøv"), "Nonmusician" = c("2", "Nonmusician", "Ikke-musiker"), "Music-loving nonmusician" = c("3", "Music-loving nonmusician", "Musikelskende ikke-musiker"), "Amateur musician" = c("4", "Amateur musician", "Amatørmusiker"), "Serious amateur musician" = c("5", "Serious amateur musician", "Seriøs amatørmusiker"), "Semiprofessional musician"= c("6", "Semiprofessional musician", "Semiprofessionel musiker"), "Professional musician" = c("7", "Professional musician", "Professionel musiker"))

df.full$personal_relation<-fct_collapse(df.full$personal_relation, No_Relation = c("0","I don’t have any particular relation to them", "Jeg har ikke nogen bestemt relation"), Relative_Friend = c("1", "I am a relative/friend", "Jeg er en ven/familie"))

# factor aware_body
df.full<-df.full%>%mutate_at(vars(matches("aware_body")), function(x){fct_collapse(x, "Not at all" = c("1", "Not at all"), "Rarely" = c("2", "Rarely", "Sjældent"), "Intermittently" = c("3", "Intermittently", "Fra tid til anden"), "Continuously" = c("4", "Continuously", "Hele tiden"))})
check<-df.full%>%select(matches("aware_body"))

# factor aware_movement
df.full<-df.full%>%mutate_at(vars(matches("aware_movement")), function(x){fct_collapse(x, "Not aware of movement" = c("1", "Not aware of movement", "Ikke opmærksom på bevægelse"),"Yes and I moved less than usual"= c("2", "1.5", "Yes and I moved less than usual", "Ja, og jeg bevægede mig mindre end normalt"), "Yes and I moved a normal amount" = c("3", "Yes and I moved a normal amount", "Ja, og jeg bevægede mig som jeg normalt ville have gjort"),"Yes and I moved more than usual" = c("4", "Yes and I moved more than usual", "Ja, og jeg bevægede mig mere end normalt"))}) # with the 1.5 value, see section on checking that the values make sense for explanation. Just one pt used it and it looks like they tried to scratch out 1 and leave 2. 

# factor aware_others_moving
df.full<-df.full%>%mutate_at(vars(matches("aware_others_moving")), function(x){fct_collapse(x, "Not aware of others' movement" = c("1", "Not aware of others&#39; movement", "Not aware of others’ movement","Not aware of others' movement", "Ikke opmærksom på andres bevægelse"),"Yes and they moved less than usual"= c("2", "Yes and they moved less than usual"), "Yes and they moved a normal amount" = c("3", "Yes and they moved a normal amount", "Ja, og de bevægede sig som de normalt ville have gjort"),"Yes and they moved more than usual" = c("4", "Yes and they moved more than usual"))})

```

## Factor those factors that were only in the virtual participants list
city, viewing with others, phone_loc
City: hard to factor. Maybe just leave as is. 
viewing_with_others: this question was written "Are you viewing the concert with anyone you know?" with the subtitle "Fill in the number of people you are viewing the concert with: "
I did not realize that the subtitle would not be written in the surveys in the app, so they only saw the main question without the subtitle. Because of this, people occasssionally wrote yes, no or reported who they were watching the concert with or "aline" which is likely a typo of "alone". I have recoded to yes or no for these purposes. 
```{r}
df.full$viewing_with_others<-fct_collapse(df.full$viewing_with_others, Yes = c("Yes", "yes", "ja", "Ja", "My cousin", "My wife", "Parents"), No = c("No","Nope", "no", "Nei","Nej", "Aline"))
df.full$phone_loc<-fct_collapse(df.full$phone_loc, Upper = c("It was located on my UPPER body", "Den befandt sig på min overkrop"), Lower = c("It was located on my LOWER body"), Other = c("Other", "Andet"))
```
## Pre-processing

### create a new ID col
```{r}
df.full<-rowid_to_column(df.full, "Pt_ID")
```

### Numeric
The virtual participants have responses like 0 (Not at all) 6 (A lot). These numbers always start the responses therefore you can extract the first number and convert to numeric. 
Create a function to extract the first number and convert to numeric.
```{r}
firstnum<-function(x) (str_sub(x, end = 1))
```

Convert numeric cols to numeric
```{r}
dfNum<-df.full%>%select(
  fan:EC_7, 
  tears_Beethoven:negatively_transformed_Beethoven,
  tears_Schnittke:negatively_transformed_Schnittke, 
  perceive:style,
  tears_Folk:negatively_transformed_Folk,
  aware_recording:changed_behaviour,
  Engage_1:Touch_4, # because I need to extract first number and factor both dfs together
  AIMS_1:AIMS_34,
  connected_audience_streaming_Beethoven:connected_audience_attending_Folk)%>%
  mutate(across(everything(),firstnum))%>%
  mutate(across(everything(),as.numeric))

df.full[names(dfNum)]<-dfNum

df.full<-df.full%>%
  mutate(age = as.numeric(age))
# NAs introduced by coercion error message because one participant wrote nonsensical letters into the age category
```

### Factor
Convert factor cols to factor.
```{r}
dfFac<-df.full%>%select(
  Pt_ID:Seat_number, 
  gender:personal_relation, 
  aware_body_Beethoven:aware_others_moving_Beethoven,
  aware_body_Schnittke:aware_others_moving_Schnittke,
  aware_body:aware_others_moving,
  aware_body_Folk:aware_others_moving_Folk,
  language:viewing_with_others,
  phone_loc)

dfFac<-dfFac%>%mutate_all(factor)

df.full[names(dfFac)]<-dfFac
```


### Check that the values make sense
When reviewing these summaries, I visually checked the min and the max values to see whether they were appropriate for the response options. 
```{r}
# summary(df.full[1:10])
# summary(df.full[11:20])
# summary(df.full[21:30])
# summary(df.full[31:40]) # check why admiration_Beethoven max = 7?
# summary(df.full[41:50])
# summary(df.full[51:60])
# summary(df.full[61:70])
# summary(df.full[71:80]) # check why admiration_Schnittke max = 7?
# summary(df.full[81:90])
# summary(df.full[91:100]) # check why negatively transformed schnittke max = 9? check why aware_movement_schnittke has one response 1.5, 
#summary(df.full[101:110]) # check why Bach Familiar max = 7 # check why style has min 1 and max 7 # check why aware_body Bach has a value of 6
# summary(df.full[111:120])  
# summary(df.full[121:130])  
# summary(df.full[131:140])  
# summary(df.full[141:150])
# summary(df.full[151:160])
# summary(df.full[161:170])
# summary(df.full[171:180])
# summary(df.full[181:190])
# summary(df.full[191:200])
# summary(df.full[201:210])
```
#### Check vars
```{r}
# check why admiration_Beethoven max = 7?
check<-df.full%>%select(ID, admiration_Beethoven)
## DSQd052 (the pt did not fill one question and the RA missed this and did not write an NA)

# check why admiration_Schnittke max = 7?
check<-df.full%>%select(ID, admiration_Schnittke)
## DSQd081 there were incorrect numbers in two places in this section...

# check why negatively transformed schnittke max = 9?
check<-df.full%>%select(ID, negatively_transformed_Schnittke)
## DSQd098 RA typed 9 when it should have been a 0

# check why aware_movement_schnittke has one response of 1.5
check<-df.full%>%select(ID, aware_movement_Schnittke)
## DSQd036 (note RA was instructed to average when two or more options are selected) It looks like they tried to scratch out 1 a little and so we can just change it to 2. I added 1.5 to the response options for the second option.

# check why Bach Familiar max = 7ø check why style has min 1 and max 7 
check<-df.full%>%select(ID, Pt_ID, familiar) 
## Turns out that the nettskjema response options were 1 (jeg har aldrig hørt det før) to 7 (jeg kender musikken ret godt). The style question has response options 1 (Jeg har aldrig hørt det før) to 7 (Jeg kender musikken ret godt). Therefore I need to change the response mapping in the virtual survey.

# check why aware_body Bach has a value of 6
check<-df.full%>%select(ID, Pt_ID, aware_body) 

# check gender dsqd132, (was written 32, pt checked kvinde)
# check aware_body_Schnittke DSQe022 (listed as 6 in the table) (turned out Maria got off track and some things were shifted in the spreadsheet.
# Check aware_body_folk DSQd097 because it is listed as 0. (again this is an issue where there was a typo/number inserted somewhere and therefore many questions were shifted)
```
All of the errors identified in the "check vars" section above have been corrected in the spreadsheet.

##### convert the response options for the Bach questions "familiar" and "style" to be able to have them on the same scale
specifically convert the virtual participants to the 0 to 6 scale by subtracting 1
```{r}
df.full<-df.full%>%mutate(familiar = ifelse(group == "Virtual", familiar-1, familiar))
df.full<-df.full%>%mutate(style = ifelse(group == "Virtual", style-1, style))
```

### TODO: check also for response bias/pts who answered the same number even on opposite items
"straight lining"
can check this with stdev functions but should probably do it on a windowed basis. Should do more searching on if there is already a function/lib that can help me. Also check out other options for checking nonsense responses or "seriousness checks" https://link.springer.com/article/10.3758/s13428-012-0265-2
Could also consider flagging if there were negative comments and then take a closer look at their responses. 
```{r}

```

### Create combined measures
Go through the surveys and create the combined measures including:
* empathic concern 
* Kama Muta 
* awe scale
* Absorption Scale - unclear how to analyze it because it is unclear what is considered high absorption versus low
* AIMS

#### Empathic Concern Scale
Note: I checked the reverse scoring in both the paper survey and the online survey and it is correct. The order of questions in this survey was slightly different from the Quarantine Concerts experiment.
```{r}
EC.df<-df.full%>%select(group,EC_1, EC_2, EC_3, EC_4, EC_5, EC_6, EC_7)

# reverse score the reversed items
columnsToReverse<-c("EC_2","EC_4","EC_5")
EC_R<-EC.df # make duplicate to check reverse scoring with
EC_R[,columnsToReverse]<-6-EC_R[,columnsToReverse]

EC.df<-EC.df%>%select(-group)
EC_R<-EC_R%>%select(-group)
# check alpha
summary(psych::alpha(EC_R))$raw_alpha
#summary(psych::alpha(EC.df))$raw_alpha # good. seems that reversing the cols helps and is detectable in alpha

#create avg value
df.full$EC<-rowMeans(EC_R, na.rm=TRUE)
```

##### Create a measure removing EC_6: I am often quite touched by things that I see happen.
I also want to check if the relations that are observed between the empathic concern scale and kama muta are in any way related to the fact that EC contains an item "I am often quite touched by things that I see happen." I thought that this could be one reason why this relation is observed. When I tested this in the exploratory analysis, empathic concern even without the item on frequently feeling touched was still highly correlated with kama muta.

```{r}
EC_R<-EC_R%>%select(-EC_6)
#create avg value
df.full$EC_noTouched<-rowMeans(EC_R, na.rm=TRUE)
```

#### AIMS
Info on AIMS: https://smartlaboratory.org/resources/aims-scale/
All items are worded in a positive direction so none need to be reversed.
```{r}
AIMS<-df.full%>%
  select(contains("AIMS"))

summary(psych::alpha(AIMS))$raw_alpha # note that alpha becomes higher with many items and it may be a poor marker of internal consistency because of the large number of items in AIMS. Still this scale has previously been tested, and therefore we do not need to worry about checking this so much.

df.full$AIMS<-rowSums(AIMS, na.rm=TRUE)
```

#### Kama Muta Scale (KAMMUS-S US)
The International Kama Muta scale was validated across 19 countries and includes the KAMMUS-2, a 22-24 item scale, instead of the 50 item version (Zickfeld, 2019).
The authors recommend that the scores of the 5 aspects should not be averaged but instead, a high score across all 5 aspects would be indicative of people experiencing this distinct social-relational emotion. However, Beate Seibt, expert on Kama Muta suggested doing a reliability analysis across all items of the short scale and averaging them if the reliability score was satisfactory.

The 5 Aspects of Being Moved Experiences are:
1. Physical sensations
2. Appraisal patterns
3. Motivation or action tendencies (telling care and wanting hug were not included because they did not seem relevant for the classical music concert context)
4. Valence
5. Labels (words used to describe kama muta - vary by culture/language. e.g. English: being moved or being touched)

##### Compute for 3 pieces
Note: could not use the "contains" short cut because "untouched" and "others_moved" were being selected as well.
```{r}
#Beethoven
KM_Beethoven<-df.full%>%
  select(tears_Beethoven:positive_Beethoven, moved_Beethoven:touched_Beethoven)

print(summary(psych::alpha(KM_Beethoven))$raw_alpha)
  
df.full$KM_Beethoven<-rowMeans(KM_Beethoven, na.rm=TRUE)

# Schnittke
KM_Schnittke<-df.full%>%
  select(tears_Schnittke:positive_Schnittke, moved_Schnittke:touched_Schnittke)

print(summary(psych::alpha(KM_Schnittke))$raw_alpha)
  
df.full$KM_Schnittke<-rowMeans(KM_Schnittke, na.rm=TRUE)

# FOlk
KM_Folk<-df.full%>%
  select(tears_Folk:positive_Folk, moved_Folk:touched_Folk)

print(summary(psych::alpha(KM_Folk))$raw_alpha)
  
df.full$KM_Folk<-rowMeans(KM_Folk, na.rm=TRUE)

```

#### Awe Scale
The awe experience scale items (AWE-S; Yaden et al., 2019) we used were the two highest loading items from the subscales of perceived vastness, physical sensations, and need for accommodation:
*Perceived Vastness*
- I felt that I was in the presence of something grand.
- I experienced something greater than myself.
*Physical sensations*
- I felt my jaw drop.
- I gasped.
*Accomodation*
- I felt challenged to mentally process what I was experiencing.
- I found it hard to comprehend the experience in full.

The items have the qIDs:
- "presence_grand", 
- "greater_than_myself",
- "jaw_drop",
- "gasped",
- "challenge_process",
- "hard_comprehend",


```{r}
#Beethoven
AWE<-df.full%>%
  select(contains("Beethoven"))%>%
  select(contains(c("presence_grand", "greater_than_myself", "jaw_drop", "gasped", "challenge_process", "hard_comprehend")))

print(summary(psych::alpha(AWE))$raw_alpha)

df.full$AWE_Beethoven<-rowMeans(AWE, na.rm=TRUE)

#Schnittke
AWE<-df.full%>%
  select(contains("Schnittke"))%>%
  select(contains(c("presence_grand", "greater_than_myself", "jaw_drop", "gasped", "challenge_process", "hard_comprehend")))

print(summary(psych::alpha(AWE))$raw_alpha)

df.full$AWE_Schnittke<-rowMeans(AWE, na.rm=TRUE)

#Folk
AWE<-df.full%>%
  select(contains("Folk"))%>%
  select(contains(c("presence_grand", "greater_than_myself", "jaw_drop", "gasped", "challenge_process", "hard_comprehend")))

print(summary(psych::alpha(AWE))$raw_alpha)

df.full$AWE_Folk<-rowMeans(AWE, na.rm=TRUE)
```
#### Create the averaged connected_audience for the virtual audience
1. Mutate only the virtual measures. 2. Recombine.
```{r}
connected_aud_df<-df.full

virt.dat<-connected_aud_df%>%filter(group == "Virtual")%>%
  mutate(connected_audience_Beethoven = (connected_audience_streaming_Beethoven+connected_audience_attending_Beethoven)/2)%>%
  mutate(connected_audience_Schnittke = (connected_audience_streaming_Schnittke+connected_audience_attending_Schnittke)/2)%>%
  mutate(connected_audience_Folk = (connected_audience_streaming_Folk+connected_audience_attending_Folk)/2)
  
live.dat<-connected_aud_df%>%filter(group == "Live")

df.full<-bind_rows(live.dat, virt.dat)
```

## Remove unnecessary columns
```{r}
drop_cols<-c("Pt_ID", "Paper Q Codes")
df.full<-df.full%>%select(! drop_cols)
```

## Move Participant Code to the beginning of the dataframe
```{r}
df.full<-df.full%>%select(ParticipantCode, everything())
```


# Save prepared data
## R format
```{r}
filename<-paste0("../output/Prepared_Data.Rda")
saveRDS(df.full, filename)
```
## CSV file
In the felles drive this appears strangely because excel is doing some text wrapping. Therefore, I made an xlsx version that can be viewed correctly.
```{r}
filename<-paste0("../output/Prepared_Data.csv")
write.csv(df.full, filename, row.names = FALSE)
```
## XLSX file
```{r}
filename<-paste0("../output/Prepared_Data.xlsx")
write.xlsx(df.full, filename,keepNA=TRUE, row.names = FALSE)
```


## Make a codebook for reference
```{r}
changeHead<-function(x){
  names(x)= c("ID", "English_Q", "Danish_Q") 
  return(x)}

codebooks<-list(codebook1, codebook2, codebook3, codebook4)
codebooks<-lapply(codebooks, changeHead)

codebook<-bind_rows(codebooks)
```
### Save codebook
```{r}
filename<-paste0("../output/Codebook.csv")
write.csv(codebook, filename, row.names = FALSE)
```

### Save comments book
```{r}
comments<-df.full%>%select(ParticipantCode,ID,userID,group,language,Comments)%>%drop_na(Comments)
filename<-paste0("../output/Qualitative_Analysis_Comments.csv")
#write.csv(comments, filename, row.names = FALSE)
filename<-paste0("../output/Qualitative_Analysis_Comments.xlsx")
write.xlsx(comments, filename, row.names = FALSE)
```


