---
title: "Exploratory Visualizations"
author: "Dana Swarbrick"
date: "24/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Import libraries

```{r libraries}
packages = c("psych", "readxl", "magrittr", "reshape2","ggpubr", "ltm","janitor", "PerformanceAnalytics", "tidyverse", "lme4")

## Now load or install&load all
package.check <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  }
)

source("useful_functions.R")
```

# Load the Data
```{r}
df.full<-readRDS(file = "../output/Prepared_Data.Rda")
```

# Explore the Data
## characterize demographics
```{r}
df.full%>%group_by(gender)%>%count()
```

### Live
```{r}
df.full%>%
  filter(group == "Live")%>%
  select(gender, age, musician_status, personal_relation, fan, EC)%>%
  summary(.)

df.full%>%filter(group == "Live")%>%
  select(musician_status)%>%
  summary(.)

# SD age
df.full%>%filter(group=="Live")%>%summarise(mean(age, na.rm= TRUE), sd(age, na.rm= TRUE))
  
# SD fan
df.full%>%filter(group=="Live")%>%summarise(mean(fan, na.rm= TRUE), sd(fan, na.rm= TRUE))

# SD EC
df.full%>%filter(group=="Live")%>%summarise(mean(EC, na.rm= TRUE), sd(EC, na.rm= TRUE))
```

### Virtual 
```{r}
df.full%>%
  filter(group == "Virtual")%>%
  select(gender, age, musician_status, personal_relation, fan, EC)%>%
  summary(.)

test<-df.full%>%filter(group == "Virtual")%>%
  select(musician_status)%>%
  summary(.)

# SD age
df.full%>%filter(group=="Virtual")%>%summarise(mean(age, na.rm= TRUE), sd(age, na.rm= TRUE))
  
# SD fan
df.full%>%filter(group=="Virtual")%>%summarise(mean(fan, na.rm= TRUE), sd(fan, na.rm= TRUE))

# SD EC
df.full%>%filter(group=="Virtual")%>%summarise(mean(EC, na.rm= TRUE), sd(EC, na.rm= TRUE))
```

#### Make a list of cities of livestreamers for a wordcloud
```{r}
# City list 
txt<-df.full%>%select(city)%>%drop_na()
filename<-paste0("../output/city_wordcloud.txt")
write.table(txt, file = filename, sep = "\t",
            row.names = FALSE)
```

# Visualizations 
Try KM and EC correlation, etc. Let's make some charts to test expected correlations.
```{r}
colours_DSQ<-c("#2d769a", "white","#b34036")
```

### Are EC and KM related, as expected?
There were no significant correlations in the virtual audience (n = 67) but there were significant correlations with the live audience (n = 91).
```{r}
df.full%>%count(group)

df.full%>%
  filter(group == "Live")%>%
  select(EC, contains('KM'))%>%
  chart.Correlation(method = "kendall")

df.full%>%
  filter(group == "Virtual")%>%
  select(EC, contains('KM'))%>%
  chart.Correlation(method = "kendall")
```

#### Try again with EC_6 removed (EC_noTouched)
No change 

Details: EC_6 is "I am often quite touched by things that I see happen."
Therefore I wanted to check that even when this item is removed, is there still a relation between KM and EC.
```{r}
df.full%>%count(group)

df.full%>%
  filter(group == "Live")%>%
  select(EC_noTouched, contains('KM'))%>%
  chart.Correlation(method = "kendall")

df.full%>%
  filter(group == "Virtual")%>%
  select(EC_noTouched, contains('KM'))%>%
  chart.Correlation(method = "kendall")
```

### How does connectedness fit in to this picture, regardless of piece
```{r}
dat<-df.full%>%select(Pt_ID, group, contains("connected"), contains("KM"), EC)

df<-dat%>%
  select(-c(connected_audience_streaming_Beethoven,connected_audience_attending_Beethoven,connected_audience_streaming_Schnittke,connected_audience_attending_Schnittke, connected_audience_streaming_Folk, connected_audience_attending_Folk))

#make long
df.long<-df%>%pivot_longer(!c(group, Pt_ID, EC),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")

df.wide<-df.long%>%pivot_wider(names_from = question, values_from = response)

df.wide%>%
  filter(group =="Live")%>%
  select(EC, KM,connected_musicians,connected_audience)%>%
  chart.Correlation(method = "kendall")

df.wide%>%
  filter(group =="Virtual")%>%
  select(EC, KM,connected_musicians,connected_audience)%>%
  chart.Correlation(method = "kendall")
```

### Cross-correlation between those items that were strongly correlated in the big cross-correlation (to examine looking at the raw data scatter plots again)
```{r}
dat<-df.full%>%select(Pt_ID, group, contains("connected"), contains("KM"), contains("positively_transformed"), contains("enjoy"),contains("absorbed_music"))

df<-dat%>%
  select(-c(connected_audience_streaming_Beethoven,connected_audience_attending_Beethoven,connected_audience_streaming_Schnittke,connected_audience_attending_Schnittke, connected_audience_streaming_Folk, connected_audience_attending_Folk))

#make long
df.long<-df%>%pivot_longer(!c(group, Pt_ID),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")

df.wide<-df.long%>%pivot_wider(names_from = question, values_from = response)

df.wide%>%
  filter(group =="Live")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")

df.wide%>%
  filter(group =="Virtual")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")
```


### Multiple comparison corrections
NOTE: this revealed that the chart.correlations are very minimally different....maybe it would be different for a chart with many more variables?
```{r}

dat<-df.wide%>%filter(group == "Live")

# choose correct vars
corData<-dat%>%
  select(Pt_ID, EC, KM, connected_musicians, connected_audience)

#select only complete
corData<-na.omit(corData)

# check number of samples
n<-length(unique(corData$Pt_ID))

# remove pt_id
corData<-corData%>%select(-Pt_ID)

title = "Live - Empathy, Kama Muta, Connectedness"
subtitle = paste0("Kendall Correlations (BH adj) (n = ", n, ")")

# create corrected p-values
corellation = adj.cor(corData, p.adjust = TRUE, p.adjust.method = "BH", threshold = 0.05, cor.method = "kendall")
pval = corellation$adj.p.values  # shows the p.values in a matrix format
thresR = corellation$threshold.r  # shows only the p value <0.05

# convert to triangle
thresR[lower.tri(thresR)]<- NA
pval[lower.tri(pval)]<- NA
#create melted values
melted_cormat<-melt(thresR,value.name = "r")
melted_pmat<-melt(pval, value.name = "p")
corPlotData<-full_join(melted_cormat, melted_pmat, by = c("Var1", "Var2"))
corPlotData$r[corPlotData$r==1]<-NA
corPlotData.c<-na.omit(corPlotData)
corPlotData.c$stars<-cut(corPlotData.c$p, breaks=c(-Inf, 0.001, 0.01, 0.05, Inf), label=c("***", "**", "*", ""))  # Create column of significance
corPlotData.c$r<-round(corPlotData.c$r,2)

# Create a ggheatmap
ggheatmap <- ggplot(corPlotData.c, aes(Var2, Var1, fill = r))+
  geom_tile(color = "white")+
  scale_fill_gradientn(
    colours = colours_DSQ,
    limits = c(-1,1)
  )+
  theme_minimal()+ 
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
  theme(axis.text.y = element_text(size = 6))+
  labs(title = title,
       subtitle = subtitle)+
  coord_fixed()

print(ggheatmap)

ggheatmap2<-ggheatmap+
  geom_text(aes(Var2, Var1, label = paste(stars,r, sep ="\n")), color = "black", size = 3) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 8),
    plot.subtitle = element_text(hjust = 0.5, size = 6),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    legend.justification = c(1, 0),
    legend.position = c(0.6, 0.8),
    legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 5, barheight = 0.4,
                               title.position = "top", title.hjust = 0.5, 
                               title.theme = element_text(size = 5),
                               label.theme = element_text(size = 5)))

print(ggheatmap2)


#cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.but needed to change the font size for this particular chart.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 8, 
       height = 8, 
       units = 'cm', 
       dpi = 500)

```

###  Beethoven
```{r}
df.full%>%
  filter(group =="Live")%>%
  select(EC, KM_Beethoven,connected_musicians_Beethoven,connected_audience_Beethoven, fan)%>%
  chart.Correlation(method = "kendall")


df.full%>%
  filter(group=="Virtual")%>%
  select(EC, KM_Beethoven,connected_musicians_Beethoven,connected_audience_streaming_Beethoven, connected_audience_attending_Beethoven, fan)%>%
  chart.Correlation(method = "kendall")
```

###  Schnittke
```{r}
df.full%>%
  filter(group =="Live")%>%
  select(EC, KM_Schnittke,connected_musicians_Schnittke,connected_audience_Schnittke, fan )%>%
  chart.Correlation(method = "kendall")

df.full%>%
  filter(group == "Virtual")%>%
  select(EC, KM_Schnittke,connected_musicians_Schnittke,connected_audience_streaming_Schnittke, connected_audience_attending_Schnittke, fan )%>%
  chart.Correlation(method = "kendall")
```

###  Folk
```{r}
df.full%>%
  filter(group =="Live")%>%
  select(EC, KM_Folk,connected_musicians_Folk,connected_audience_Folk, fan )%>%
  chart.Correlation(method = "kendall")

df.full%>%
  filter(group == "Virtual")%>%
  select(EC, KM_Folk,connected_musicians_Folk,connected_audience_streaming_Folk, connected_audience_attending_Folk, fan )%>%
  chart.Correlation(method = "kendall")
```

## Kama Muta: A closer look

```{r}
dat<-df.full%>%
  select(contains(c('group', 'Pt_ID', 'piece','tears','choked_up','chills','warm_feeling','welcoming','closeness','refreshed','positive','moved','touched'))) # remove kama muta vars except for  "positive" because I want to see the positive versus negative

#Beethoven
KM_Beethoven<-df.full%>%
  select(group, Pt_ID, tears_Beethoven:positive_Beethoven, moved_Beethoven:touched_Beethoven)

# Schnittke
KM_Schnittke<-df.full%>%
  select(group, Pt_ID, tears_Schnittke:positive_Schnittke, moved_Schnittke:touched_Schnittke)

# FOlk
KM_Folk<-df.full%>%
  select(group, Pt_ID, tears_Folk:positive_Folk, moved_Folk:touched_Folk)
  
# save charts

Title = "Beethoven_Live"

graphname<-paste0("../plots/KamaMuta_CC_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

KM_Beethoven%>%filter(group == "Live")%>%
  select(-c(group, Pt_ID))%>%
  chart.Correlation(method = "kendall")

dev.off()

Title = "Beethoven_Virtual"

graphname<-paste0("../plots/KamaMuta_CC_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

KM_Beethoven%>%filter(group == "Virtual")%>%
  select(-c(group, Pt_ID))%>%
  chart.Correlation(method = "kendall")

dev.off()

Title = "Schnittke_Live"

graphname<-paste0("../plots/KamaMuta_CC_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

KM_Schnittke%>%filter(group == "Live")%>%
  select(-c(group, Pt_ID))%>%
  chart.Correlation(method = "kendall")

dev.off()

Title = "Schnittke_Virtual"

graphname<-paste0("../plots/KamaMuta_CC_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

KM_Schnittke%>%filter(group == "Virtual")%>%
  select(-c(group, Pt_ID))%>%
  chart.Correlation(method = "kendall")

dev.off()

Title = "Folk_Live"

graphname<-paste0("../plots/KamaMuta_CC_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

KM_Folk%>%filter(group == "Live")%>%
  select(-c(group, Pt_ID))%>%
  chart.Correlation(method = "kendall")

dev.off()

Title = "Folk_Virtual"

graphname<-paste0("../plots/KamaMuta_CC_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

KM_Folk%>%filter(group == "Virtual")%>%
  select(-c(group, Pt_ID))%>%
  chart.Correlation(method = "kendall")

dev.off()

```


## Cross-correlations for the absorption items and aggregate measures
### Regardless of piece
```{r}
dat<-df.full%>%
  select(-contains(c('tears','chills','warm_feeling','choked_up','refreshed','welcoming','closeness','moved','touched')))%>% # remove kama muta vars except for  "positive" because I want to see the positive versus negative association and I don't want to remove the positively transformed one. 
  select(-contains(c('presence_grand','greater_than_myself','jaw_drop','gasped','challenge_process','hard_comprehend')))%>% # remove awe vars
  select(-contains('aware'))# because these are factors (but could actually be converted to ordinal)

virt.dat<-dat%>%filter(group == "Virtual")%>%
  mutate(connected_audience_Beethoven = (connected_audience_streaming_Beethoven+connected_audience_attending_Beethoven)/2)%>%
  mutate(connected_audience_Schnittke = (connected_audience_streaming_Schnittke+connected_audience_attending_Schnittke)/2)%>%
  mutate(connected_audience_Folk = (connected_audience_streaming_Folk+connected_audience_attending_Folk)/2)
  
           
live.dat<-dat%>%filter(group == "Live")

df<-bind_rows(live.dat, virt.dat)%>%
  select(-c(connected_audience_streaming_Beethoven,connected_audience_attending_Beethoven,connected_audience_streaming_Schnittke,connected_audience_attending_Schnittke, connected_audience_streaming_Folk, connected_audience_attending_Folk))
  
cor.df<-df%>%select(group, Pt_ID, EC, AIMS, fan, positive_Beethoven:negatively_transformed_Schnittke, positive_Folk:negatively_transformed_Folk, KM_Beethoven: AWE_Folk)

#make long
df.long<-cor.df%>%pivot_longer(!c(group, Pt_ID, EC, AIMS, fan),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")

df.wide<-df.long%>%pivot_wider(names_from = question, values_from = response)

df.cor<-df.wide%>%
  filter(group =="Live")%>%
  select(-c(group,Pt_ID))

#  chart.Correlation(method = "kendall")

#select only complete
corData<-na.omit(df.cor)

# check number of samples
samples<-nrow(corData)

title = "Live (Regardless of Piece)" # UPDATE
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 10, 
       units = 'cm', 
       dpi = 500)

df.cor<-df.wide%>%
  filter(group =="Virtual")%>%
  select(-c(group,Pt_ID))

#  chart.Correlation(method = "kendall")

#select only complete
corData<-na.omit(df.cor)

# check number of samples
samples<-nrow(corData)

title = "Virtual (Regardless of Piece)" # UPDATE
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 10, 
       units = 'cm', 
       dpi = 500)
```

### Beethoven 
Especially examine absorption's relation to other things. Remove vars that are represented in other vars like KM vars, AWE, and vars that are not numeric like the awareness ones. 

#### Live
```{r}
corData<-df.full%>% # without including the KM vars, awe vars, and aware vars
  filter(group == "Live")%>%
  select(EC, fan, group, AIMS, contains('Beethoven'))%>%
  select(-contains(c('tears','chills','warm_feeling','choked_up','refreshed','welcoming','closeness','moved','touched')))%>% # remove kama muta vars except for  "positive" because I want to see the positive versus negative association and I don't want to remove the positively transformed one. 
  select(-contains(c('presence_grand','greater_than_myself','jaw_drop','gasped','challenge_process','hard_comprehend')))%>%
  select(-contains('aware'))%>%# because these are factors (but could actually be converted to ordinal)
  select(-contains('connected')) # because the connected measure needs to be re-worked a little

#select only complete
corData<-na.omit(corData)

# check number of samples
samples<-nrow(corData)

title = "Beethoven Live"
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

### quickly check if the values are the same with chart.correlation
corData%>%select(-group)%>%chart.Correlation(method = "kendall") # no, less items are shown as significant with the multiple comparison corrections even though the correlation values are the same, it is the p-value being adjusted. 

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

#### Virtual 
```{r}
corData<-df.full%>% # without including the KM vars, awe vars, and aware vars
  filter(group == "Virtual")%>% # UPDATE
  select(EC, fan, group, contains('Beethoven'))%>% # UPDATE # removed AIMS because it 
  select(-contains(c('tears','chills','warm_feeling','choked_up','refreshed','welcoming','closeness','moved','touched')))%>% # remove kama muta vars except for  "positive" because I want to see the positive versus negative association and I don't want to remove the positively transformed one. 
  select(-contains(c('presence_grand','greater_than_myself','jaw_drop','gasped','challenge_process','hard_comprehend')))%>%
  select(-contains('aware'))%>%# because these are factors (but could actually be converted to ordinal)
  select(-contains('connected')) # because the connected measure needs to be re-worked a little

#select only complete
corData<-na.omit(corData)

# check number of samples
samples<-nrow(corData)

title = "Beethoven Virtual" # UPDATE
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

### Schnittke
#### Live
```{r}
corData<-df.full%>% # without including the KM vars, awe vars, and aware vars
  filter(group == "Live")%>%
  select(ID,EC, fan, group, AIMS, contains('Schnittke'))%>%
  select(-contains(c('tears','chills','warm_feeling','choked_up','refreshed','welcoming','closeness','moved','touched')))%>% # remove kama muta vars except for  "positive" because I want to see the positive versus negative association and I don't want to remove the positively transformed one. 
  select(-contains(c('presence_grand','greater_than_myself','jaw_drop','gasped','challenge_process','hard_comprehend')))%>%
  select(-contains('aware'))%>%# because these are factors (but could actually be converted to ordinal)
  select(-contains('connected'))%>% # because the connected measure needs to be re-worked a little
  select(-contains('relaxed')) # because this was forgotten in the English survey

#select only complete
corData<-na.omit(corData)

# check number of samples
samples<-nrow(corData)

title = "Schnittke Live"
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

#### Virtual 
```{r}
corData<-df.full%>% # without including the KM vars, awe vars, and aware vars
  filter(group == "Virtual")%>% # UPDATE
  select(EC, fan, group, contains('Schnittke'))%>% # UPDATE
  select(-contains(c('tears','chills','warm_feeling','choked_up','refreshed','welcoming','closeness','moved','touched')))%>% # remove kama muta vars except for  "positive" because I want to see the positive versus negative association and I don't want to remove the positively transformed one. 
  select(-contains(c('presence_grand','greater_than_myself','jaw_drop','gasped','challenge_process','hard_comprehend')))%>%
  select(-contains('aware'))%>%# because these are factors (but could actually be converted to ordinal)
  select(-contains('connected')) # because the connected measure needs to be re-worked a little

#select only complete
corData<-na.omit(corData)

# check number of samples
samples<-nrow(corData)

title = "Schnittke Virtual" # UPDATE
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

### Folk
#### Live
```{r}
corData<-df.full%>% # without including the KM vars, awe vars, and aware vars
  filter(group == "Live")%>%
  select(EC, fan, group, AIMS, contains('Folk'))%>%
  select(-contains(c('tears','chills','warm_feeling','choked_up','refreshed','welcoming','closeness','moved','touched')))%>% # remove kama muta vars except for  "positive" because I want to see the positive versus negative association and I don't want to remove the positively transformed one. 
  select(-contains(c('presence_grand','greater_than_myself','jaw_drop','gasped','challenge_process','hard_comprehend')))%>%
  select(-contains('aware'))%>%# because these are factors (but could actually be converted to ordinal)
  select(-contains('connected'))%>% # because the connected measure needs to be re-worked a little
  select(-contains('relaxed')) # because this was forgotten in the English survey

#select only complete
corData<-na.omit(corData)

# check number of samples
samples<-nrow(corData)

title = "Folk Live"
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

#### Virtual 
```{r}
corData<-df.full%>% # without including the KM vars, awe vars, and aware vars
  filter(group == "Virtual")%>% # UPDATE
  select(EC, fan, group, contains('Folk'))%>% # UPDATE
  select(-contains(c('tears','chills','warm_feeling','choked_up','refreshed','welcoming','closeness','moved','touched')))%>% # remove kama muta vars except for  "positive" because I want to see the positive versus negative association and I don't want to remove the positively transformed one. 
  select(-contains(c('presence_grand','greater_than_myself','jaw_drop','gasped','challenge_process','hard_comprehend')))%>%
  select(-contains('aware'))%>%# because these are factors (but could actually be converted to ordinal)
  select(-contains('connected')) # because the connected measure needs to be re-worked a little

#select only complete
corData<-na.omit(corData)

# check number of samples
samples<-nrow(corData)

title = "Folk Virtual" # UPDATE
subtitle = paste0("Kendall Correlations (BH adj) (n = ", samples, ")")
cross.correlation(corData, colours_DSQ, title, subtitle) #moved the cross-correlation code to the useful_functions script to make this more tidy.

graphname<-paste0("../plots/Kendall-Correlations-", title, ".png")
ggsave(graphname, 
       width = 10, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

## Prelim Bach Visualization findings
```{r}
Title = "Bach Visualization"

dat<-df.full%>%
  select(EC, group, fan, perceive:style)

c<-dat%>%
  group_by(group)%>%
  count()

Subtitle = paste0("n live = ", c$n[c$group =="Live"], "; n virtual = ", c$n[c$group =="Virtual"])

dat_long<-dat%>%
  pivot_longer(!c(EC, group, fan), names_to = "question", values_to = "response")

dat_long$question[dat_long$question == "emotionally_moved"]<-"moved"

dat_long%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_boxplot()+
  labs(title=Title,
       subtitle = Subtitle)+
  theme_DSQ()
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=1)+
  #geom_boxplot(width = 0.1, fill = "white")

graphname<-paste0("../plots/",Title, ".png")
ggsave(graphname, 
       width = 20, 
       height = 9, 
       units = 'cm', 
       dpi = 500)

dat_long%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_violin()+
  labs(title=Title,
       subtitle = Subtitle)#+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=1)+
  #geom_boxplot(width = 0.1, fill = "white")

graphname<-paste0("../plots/Violin_",Title, ".png")
ggsave(graphname, 
       width = 30, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```


## Prelim absorption findings
```{r}

absorb.items<-c("own_world", "absorbed_music", "daydream", "sense_time", "distracted", "attentive", "attention_others","attention_sensations", "transformed")

absorb<-df.full%>%
  select(group, Pt_ID, contains(absorb.items))

absorb.long<-absorb%>%pivot_longer(!c(group,Pt_ID),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")
```

### Beethoven
```{r}
Title = "Absorption Beethoven"

absorb.beethoven<-absorb.long%>%
  filter(piece == "Beethoven")%>%
  drop_na()

c<-absorb.beethoven%>%
  group_by(group)%>%
  count()

Subtitle = paste0("n live = ~", round(c$n[c$group =="Live"]/length(absorb.items),1), "; n virtual = ~", round(c$n[c$group =="Virtual"]/length(absorb.items),1))
# round because decimal because sometimes people didn't answer every question. There should be a way to get a better estimate of this btw, for example including ids and then counting the number of unique IDs.

absorb.beethoven%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_boxplot()+
  labs(title=Title,
       subtitle = Subtitle)+
  theme_DSQ()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))


graphname<-paste0("../plots/",Title, ".png")
ggsave(graphname, 
       width = 20, 
       height = 13, 
       units = 'cm', 
       dpi = 500)

absorb.beethoven%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_violin()+
  labs(title=Title,
       subtitle = Subtitle)#+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=1)+
  #geom_boxplot(width = 0.1, fill = "white")

graphname<-paste0("../plots/Violin_",Title, ".png")
ggsave(graphname, 
       width = 30, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

### Schnittke
```{r}
Title = "Absorption Schnittke"

absorb.schnittke<-absorb.long%>%
  filter(piece == "Schnittke")%>%
  drop_na()%>%
  filter(response<7)

c<-absorb.schnittke%>%
  group_by(group)%>%
  count()

Subtitle = paste0("n live = ~", round(c$n[c$group =="Live"]/length(absorb.items),1), "; n virtual = ~", round(c$n[c$group =="Virtual"]/length(absorb.items),1))
# round because decimal because sometimes people didn't answer every question. There should be a way to get a better estimate of this btw, for example including ids and then counting the number of unique IDs.

absorb.schnittke%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_boxplot()+
  labs(title=Title,
       subtitle = Subtitle)+
  theme_DSQ()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))

graphname<-paste0("../plots/",Title, ".png")
ggsave(graphname, 
       width = 20, 
       height = 13, 
       units = 'cm', 
       dpi = 500)

absorb.schnittke%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_violin()+
  labs(title=Title,
       subtitle = Subtitle)#+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=1)+
  #geom_boxplot(width = 0.1, fill = "white")

graphname<-paste0("../plots/Violin_",Title, ".png")
ggsave(graphname, 
       width = 30, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

### Folk
```{r}
Title = "Absorption Folk"

absorb.folk<-absorb.long%>%
  filter(piece == "Folk")%>%
  drop_na()

c<-absorb.folk%>%
  group_by(group)%>%
  count()

Subtitle = paste0("n live = ~", round(c$n[c$group =="Live"]/length(absorb.items),1), "; n virtual = ~", round(c$n[c$group =="Virtual"]/length(absorb.items),1))
# round because decimal because sometimes people didn't answer every question. There should be a way to get a better estimate of this btw, for example including ids and then counting the number of unique IDs.

absorb.folk%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_boxplot()+
  labs(title=Title,
       subtitle = Subtitle)+
  theme_DSQ()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45))

graphname<-paste0("../plots/",Title, ".png")
ggsave(graphname, 
       width = 20, 
       height = 13, 
       units = 'cm', 
       dpi = 500)

absorb.folk%>%ggplot(aes(fill = group,x = question, y = response))+
  geom_violin()+
  labs(title=Title,
       subtitle = Subtitle)#+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=1)+
  #geom_boxplot(width = 0.1, fill = "white")

graphname<-paste0("../plots/Violin_",Title, ".png")
ggsave(graphname, 
       width = 30, 
       height = 9, 
       units = 'cm', 
       dpi = 500)
```

## Aware of movement
```{r}
aware.items<-c("aware_body", "aware_movement", "aware_others_moving")
aware<-df.full%>%
  select(group, Pt_ID, contains(aware.items))

aware<-aware%>%rename(aware_body_Bach = aware_body,
                      aware_movement_Bach = aware_movement,
                      aware_others_moving_Bach = aware_others_moving)

aware.long<-aware%>%pivot_longer(!c(group,Pt_ID),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")

aware.long$piece<-factor(aware.long$piece, levels = c("Beethoven", "Schnittke", "Bach", "Folk")) #factor for the correct facet order

## AWARE BODY
aware_body.long<-aware.long%>%filter(question == "aware_body")%>%filter(response %in% c("Not at all", "Rarely", "Intermittently", "Continuously"))

Title = "Aware Body"

ggplot(aware_body.long, aes(x = response, fill = group))+
  geom_histogram( stat = "density", position= position_dodge(preserve = "single"))+
  labs(title = Title)+
  theme_minimal()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
  facet_grid(piece ~ group)

graphname<-paste0("../plots/Histogram ",Title, ".png")
ggsave(graphname, 
       width = 11, 
       height = 13, 
       units = 'cm', 
       dpi = 500)

## AWARE MOVEMENT
aware_movement.long<-aware.long%>%filter(question == "aware_movement")%>%drop_na()%>%filter(!response %in% c("1.5"))

Title = "Aware Movement"

ggplot(aware_movement.long, aes(x = response, fill = group))+
  geom_histogram( stat = "count", position= position_dodge(preserve = "single"))+
  labs(title = Title)+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  theme_minimal()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
  facet_grid(piece ~ group)

graphname<-paste0("../plots/Histogram ",Title, ".png")
ggsave(graphname, 
       width = 11, 
       height = 13, 
       units = 'cm', 
       dpi = 500)

## AWARE OTHERS MOVING
aware_others_movement.long<-aware.long%>%filter(question == "aware_others_moving")%>%drop_na()

Title = "Aware Others Moving"

ggplot(aware_others_movement.long, aes(x = response, fill = group))+
  geom_histogram( stat = "count", position= position_dodge(preserve = "single"))+
  labs(title = Title)+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20))+
  theme_minimal()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
  facet_grid(piece ~ group)

graphname<-paste0("../plots/Histogram ",Title, ".png")
ggsave(graphname, 
       width = 11, 
       height = 13, 
       units = 'cm', 
       dpi = 500)
```

## Live versus livestreamed
```{r}
dat<-df.full%>%select(Pt_ID, group, contains("connected"))

# virt.dat<-dat%>%filter(group == "Virtual")%>%
#   mutate(connected_audience_Beethoven = (connected_audience_streaming_Beethoven+connected_audience_attending_Beethoven)/2)%>%
#   mutate(connected_audience_Schnittke = (connected_audience_streaming_Schnittke+connected_audience_attending_Schnittke)/2)%>%
#   mutate(connected_audience_Folk = (connected_audience_streaming_Folk+connected_audience_attending_Folk)/2)
#   
#            
# live.dat<-dat%>%filter(group == "Live")
# 
# df<-bind_rows(live.dat, virt.dat)%>%
#   select(-c(connected_audience_streaming_Beethoven,connected_audience_attending_Beethoven,connected_audience_streaming_Schnittke,connected_audience_attending_Schnittke, connected_audience_streaming_Folk, connected_audience_attending_Folk))

#make long
df.long<-dat%>%pivot_longer(!c(group, Pt_ID),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")

df.wide<-df.long%>%pivot_wider(names_from = question, values_from = response)

df.long$piece<-factor(df.long$piece, levels = c("Beethoven", "Schnittke", "Bach", "Folk")) #factor for the correct facet order


Title = "Connected to Musicians"
conn.musicians<-df.long%>%filter(question == "connected_musicians")%>%drop_na()

ggplot(conn.musicians, aes(x = response, y = stat(width*density), fill = group))+
  geom_histogram(position= position_dodge(preserve = "single"))+
  labs(title = Title)+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  theme_minimal()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
  facet_grid(piece ~ group)

```

## Cross-correlation on absorption items
### kama muta versus ...
trait empathy and absorption relation?
include empathy and all items in the absorption measure
```{r}

absorb.items<-c("own_world", "absorbed_music", "daydream", "sense_time", "distracted", "attentive", "attention_others","attention_sensations", "transformed")

absorb<-df.full%>%
  select(group, Pt_ID, EC, AIMS, contains(absorb.items))

absorb.long<-absorb%>%pivot_longer(!c(group,Pt_ID, EC, AIMS),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")

absorb.wide<-absorb.long%>%pivot_wider(names_from = question, values_from = response)

absorb.beethoven<-absorb.wide%>%
  filter(piece == "Beethoven")%>%
  drop_na()

absorb.schnittke<-absorb.wide%>%
  filter(piece == "Schnittke")%>%
  drop_na()

absorb.folk<-absorb.wide%>%
  filter(piece == "Folk")%>%
  drop_na()

## Save plots: Beethoven 

Title = "Beethoven_Live"

graphname<-paste0("../plots/CrossCorr_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

absorb.beethoven%>%
  filter(group =="Live")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")

dev.off()

##

Title = "Beethoven_Virtual"

graphname<-paste0("../plots/CrossCorr_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

absorb.beethoven%>%
  filter(group =="Virtual")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")

dev.off()

## Save plots: Schnittke 

Title = "Schnittke_Live"

graphname<-paste0("../plots/CrossCorr_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

absorb.schnittke%>%
  filter(group =="Live")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")

dev.off()

##

Title = "Schnittke_Virtual"

graphname<-paste0("../plots/CrossCorr_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

absorb.schnittke%>%
  filter(group =="Virtual")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")

dev.off()

## Save plots: Folk 

Title = "Folk_Live"

graphname<-paste0("../plots/CrossCorr_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

absorb.folk%>%
  filter(group =="Live")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")

dev.off()

##

Title = "Folk_Virtual"

graphname<-paste0("../plots/CrossCorr_",Title, ".jpg")

jpeg(graphname, width = 1500, height = 1500)

absorb.folk%>%
  filter(group =="Virtual")%>%
  select(-c(Pt_ID, group, piece))%>%
  chart.Correlation(method = "kendall")

dev.off()

```


# Comments
```{r}
comments<-df.full%>%select(group,language,Pt_ID, Comments)
```

## Add a tag of negative or positive and then see if that influences people's average survey responses (generally). Perhaps this could act as a bit of a respondent "seriousness check". (i.e. if they were expecting a normal concert or a science concert)

## Others moved
"To what extent do you believe audience members around you were moved?"
0 (Not at all) - 6 (A lot)
```{r}
moved<-df.full%>%
  select(contains("moved"), EC, contains("connected_audience"), group)%>%
  select(-"emotionally_moved", -contains(c("attending", "streaming")))
```
### check for similarity
1) subtract report of others from their own report
2) absolute value
3) check how empathy is correlated
```{r}
moved$similarity_Beethoven<-moved$moved_Beethoven-moved$others_moved_Beethoven
moved$similarity_Beethoven<-abs(moved$similarity_Beethoven)
summary(moved$similarity_Beethoven)

moved$similarity_Schnittke<-moved$moved_Schnittke-moved$others_moved_Schnittke
moved$similarity_Schnittke<-abs(moved$similarity_Schnittke)
summary(moved$similarity_Schnittke)

moved$similarity_Folk<-moved$moved_Folk-moved$others_moved_Folk
moved$similarity_Folk<-abs(moved$similarity_Folk)
summary(moved$similarity_Folk)

# make a scatterplot examining EC and similarity
moved%>%
  select(EC, contains("similarity"))%>%
  chart.Correlation(method = "kendall")
```
The chart suggests that there is no correlation between empathic concern and similarity.
What else can lead to increased reports of similarity?
- try connectedness

```{r}
# make a scatterplot examining connectedness and similarity
moved%>%
  select(-EC, -contains("moved"))%>%
  chart.Correlation(method = "kendall")
```
Connectedness to the audience felt during Beethoven led to more similar reports of feeling moved and how much they thought others were moved. Negative correlations indicate that the more connected they felt, the more similar the felt (because similarity is a difference). BUT WEIRD: connectedness in Beethoven but not Schnittke was correlated with how similar pts reports were of feeling moved in Schnittke. 
Strongest cor: connectedness to the audience and similarity in the Folk which is also the piece that made people feel most moved?

## What about when comparing live and virtual separately?
### Live
```{r}
moved%>%
  filter(group == "Live")%>%
  select(EC, contains("similarity"))%>%
  chart.Correlation(method = "kendall")
```
### Virtual
The virtua group had a really strong positive correlation between empathic concern and similarity which indicates that the more empathic concern a person had, they rated the other audience members as less similar in feeling moved. The sample is quite small though...
```{r}
moved%>%
  filter(group == "Virtual")%>%
  select(EC, contains("similarity"))%>%
  chart.Correlation(method = "kendall")

```
## Similarity and connectedness separated by group
### Live
```{r}
moved%>%
  filter(group == "Live")%>%
  select(-group, -EC, -contains("moved"))%>%
  chart.Correlation(method = "kendall")
```
### Virtual
```{r}
moved%>%
  filter(group == "Virtual")%>%
  select(-group, -EC, -contains("moved"))

%>%
  chart.Correlation(method = "kendall")
```

## Lumping all pieces together
```{r}

```


