---
title: "Statistical Analysis"
author: "Dana Swarbrick"
date: "24/11/2021"
output: html_document
---

TODO: Investigate using rmcorr: https://www.frontiersin.org/articles/10.3389/fpsyg.2017.00456/full

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Live versus Livestreamed: Do people in the live concert feel more connected than people watching a virtual concert?
IV: live versus virtual
DV: connectedness (ordinal)

## First let's look at raw data
```{r}
df.long%>%filter(question == "connected_musicians")%>%
  ggplot(aes(x = group, y = response, fill = group))+
    geom_dotplot(binaxis = "y", stackdir = "center", position = "dodge", dotsize = 0.45)

df.long%>%filter(question == "connected_musicians")%>%
  ggplot(aes(x = group, y = response, fill = group))+
    geom_violin()
```

```{r}
Title = "Connectedness"

ggplot(df.long, aes(x = question, y = response, fill = group))+
  geom_boxplot(position= position_dodge(preserve = "single"))+
  labs(title = Title)+
  scale_x_discrete(labels =  function(x) str_wrap(str_replace_all(x, "_", " "), width = 15))+
  theme_minimal()+
  theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
  facet_grid(piece ~ .)


graphname<-paste0("../plots/Boxplot ",Title, ".png")
ggsave(graphname, 
       width = 13, 
       height = 13, 
       units = 'cm', 
       dpi = 500)

# position dodge does not work for violin plots so I could make two separate for audience and musicians
df.long%>%filter(grepl("audience", question))%>%
  ggplot(aes(x = question, y = response, fill = group))+
    geom_violin()+
    labs(title = Title)+
    scale_x_discrete(labels =  function(x) str_wrap(str_replace_all(x, "_", " "), width = 15))+
    theme_minimal()+
    theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
    facet_grid(piece ~ .)

df.long%>%filter(grepl("musicians", question))%>%
  ggplot(aes(x = question, y = response, fill = group))+
    geom_violin()+
    labs(title = Title)+
    scale_x_discrete(labels =  function(x) str_wrap(str_replace_all(x, "_", " "), width = 15))+
    theme_minimal()+
    theme(axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 6))+
    facet_grid(piece ~ .)

```

## Now let's run some stats
IV: live versus virtual; audience vs musicians?
DV: connectedness (ordinal)
```{r}
dat<-df.full%>%select(Pt_ID, group, contains("connected"))

virt.dat<-dat%>%filter(group == "Virtual")%>%
  mutate(connected_audience_Beethoven = (connected_audience_streaming_Beethoven+connected_audience_attending_Beethoven)/2)%>%
  mutate(connected_audience_Schnittke = (connected_audience_streaming_Schnittke+connected_audience_attending_Schnittke)/2)%>%
  mutate(connected_audience_Folk = (connected_audience_streaming_Folk+connected_audience_attending_Folk)/2)


live.dat<-dat%>%filter(group == "Live")

df<-bind_rows(live.dat, virt.dat)%>%
  select(-c(connected_audience_streaming_Beethoven,connected_audience_attending_Beethoven,connected_audience_streaming_Schnittke,connected_audience_attending_Schnittke, connected_audience_streaming_Folk, connected_audience_attending_Folk))

#make long
df.long<-df%>%pivot_longer(!c(group, Pt_ID),
                        names_to = c("question", "piece"),
                        names_pattern ="(.*)_(.*)",
                        values_to = "response")

df.long$piece<-factor(df.long$piece, levels = c("Beethoven", "Schnittke", "Bach", "Folk")) #factor for the correct facet order

# what is the effect of group on connectedness?
m1<-lm(response ~ group, data = df.long)
summary(m1)

m2<-lm(response ~ group+question, data = df.long)
summary(m2)

m3<-lm(response ~ group*question, data = df.long)
summary(m3)

m4<-lm(response ~ group + question + piece, data = df.long)
summary(m4)

aov(m1, m2, m3, m4)

m1<-lmer(response ~ group + (1|Pt_ID), data = df.long)
summary(m1)

m2<-lmer(response ~ group+question, data = df.long)
summary(m2)

m3<-lm(response ~ group*question, data = df.long)
summary(m3)

m4<-lm(response ~ group + question + piece, data = df.long)
summary(m4)


```

According to my stats textbook another option is a repeated measures anova

```{r}
library(ez)
data<-df.long%>%drop_na()

ezMod<-ezMixed(data = data, dv = .(response), random = .(Pt_ID), fixed = .(question, group)) # ezANOVA wasn't working with missing data
summary(ezMod)
print(ezMod$summary)
```

## tutorial from textbook.
ch. 14. I think he is using the lme function from nlme package
```{r}
library(nlme)

baseline<-lme(response ~ 1, random = ~1|Pt_ID/question/group, data = data, method = "ML") # ML = maximum likelihood estimate
groupM<-update(baseline, .~. +group)
questionM<-update(groupM, .~. +question)
pieceM<-update(questionM, .~. +piece)
group_question<-update(pieceM, .~. +group:question)
group_piece<-update(group_question, .~. +group:piece)
question_piece<-update(group_piece, .~. +question:piece)
concertM<-update(question_piece, .~. +group:question:piece)

anova(baseline, groupM, questionM, pieceM, group_question, group_piece, question_piece, concertM)

summary(concertM)
```

## show interaction ofgroup and question
```{r}
d<-data%>%group_by(Pt_ID, group, question)%>%summarise(avg = mean(response))
d%>%ggplot(aes(x = question, y = avg, fill = group))+
  geom_boxplot()
```

## factorial repeated-measures designs as a GLM
```{r}
baseline<-lmer(response ~ 1 + (1|Pt_ID), data = df.long)
```